Clicks and Cliques

### 2018-12-28 papersoul.Rnw
life chunk: fix design wt

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res + QD1 + CCE, ~QSB, des.wt, svymean, keep.var = TRUE, na.rm = T)
lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
life %<>%
  mutate(QSB = factor(QSB, levels = rev(levels(QSB))))

>>>>

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!

des.life <- soul.red2 %>% 
  filter(!is.na(WEIGHT), prop.res <= 1) %>% 
  mutate(pr = WEIGHT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .)

life <- svyby(~prop.res + QD1 + CCE, ~QSB, 
               design = des.life, svymean, keep.var = TRUE, na.rm = T)

lifevar <- svyby(~prop.res + CCE, ~QSB, des.life, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
# life %<>%
#   mutate(QSB = factor(QSB, levels = rev(levels(QSB))))
